\section{Introduction} \label{sec:introduction}
The \$42.5 billion Broadband Equity, Access, and Deployment (BEAD) Program has the potential 
to transform broadband access across the United States. It is aimed at expanding high-speed internet, 
particularly in rural areas with persistent connectivity gaps, addressing the affordability and 
accessibility issue with internet access. 
Recent policy shifts have sparked debates with their adoption of a technology-neutral approach
that redirects significant funding towards satellite providers like Starlink.
Advocates of fiber optic broadband argue that BEAD funding should prioritize 
technologies with proven reliability and scalability, such as fiber optics, 
which can deliver consistent high-speed connections with low latency.

With this in mind, our paper challenges a fundamental misconception: high throughput 
is synonymous with high-quality service. We deploy Raspberry Pi devices across the United States and collect
join throughput and latency measurements. We find that throughput is not a reliable indicator 
of network quality, especially for fixed wireless connections. Fixed wireless networks demonstrate 
very little correlation between these two factors. Latency fluctuates dramatically, and these fluctuations 
are not captured by speed metrics alone.

Our study focuses on three major fixed wireless and satellite providers—Starlink, T-Mobile, and Verizon—and 
compares their performance to traditional wired ISPs. The divergence in performance that we discover sparks the 
question if high throughput relates to a high quality user connection. 

This paper makes the following contributions:
- We develop the first method to jointly and continuously measure the performance of wired and fixed wireless
ISPs in home networks, collecting latency and throughput measurements. 
- We demonstrate that throughput is not a reliable indicator of network quality for fixed wireless connections.
Latency is a critical factor to consider.
- We provide empirical evidence of the lack of correlation between latency and throughput in fixed wireless and satellite connections.

https://statescoop.com/speed-bead-broadband-bill-starlink-2025/
